### 2010-05-05 docs/FAQ/faq.tex
add Ann's answer to Brendan's pi time-centering question

  The code is already instrumented with timers.  Simply compile with
  {\tt PROF=TRUE} in the {\tt GNUmakefile}, or equvalently do 
  {\tt make PROF=t}

@@

>>>>

  The code is already instrumented with timers.  Simply compile with
  {\tt PROF=TRUE} in the {\tt GNUmakefile}, or equvalently do 
  {\tt make PROF=t}.  A file containing a summary of the timings will
  be output in the run directory.

  An alternate way to get single-processor timings, when using 
  the GCC compilers is to add {\tt -pg} to the compilation flags
  for both {\tt gfortran} and {\tt gcc}.  Upon completion, a
  file names {\tt gmon.out} will be produced.  This can be 
  processed by {\tt gprof} running

  {\tt~~~ gprof} {\em exec-name}

  where {\em exec-name} is the name of the executable.

@@

\section{Algorithm}

\item {\em In the final projection in the algorithm, we project
  $U^{n+1}$, using a time-centered $\beta_0$, a time-centered $\rho_0$, but
  an ``$n+1$''-centered $S$.  When then is the resulting $\phi$ (which then
  defines $\pi$) is at ``$n+1/2$''?}

  The short answer to this question is that you should think of this
  as really projecting  $(U^{n+1} - U^n)$ and the right hand side as having
  $(S^{n+1} - S^n)$.  This is because the pressure enters the dynamic equations as
  $(U^{n+1} - U^n) = \ldots + \frac{1}{\rho^{n+1/2}} \nabla \pi^{n+1/2}$.
  (We approximate $\pi^{n+1/2}$ by $\pi^{n-1/2}$ then do the projection to fix the
  $\pi$ as well as the $U$.)

  So everything is in fact time-centered.
